\chapter{External services and Libraries}
\label{chap:externalServices}
We used many external services and libraries, some of them are useful to implement the core of the application, such as Firebase, while others just enhance the user experience. 

Integrating these external services we didn't need to reimplement that functionalities by our own and since they are specialised in their field their efficiency is much higher. 
\section{Firebase}
\subsection{Authentication}
This service of course represent the main entrance of the application since it handles the authentication process of users. It was very simple to implement because it requires just client-side code and it allows users to register or login with the classic email and password method or GitHub OAuth. The server-side of the application simply verify that the credential inserted are corrected and allows the user to log in.
\subsection{Database}
The Database provided by Firebase is of the NoSQL type and has several advantages: data can be updated directly in th Web Console or through a simple program, Flutter provides simple APIs to interact with it asynchronously and everything is stored in the Firebase's cloud. 

We use it to store different type of cars, charging stations with their location and properties, users with their saved settings(i.e. name and car) and all the recharges made. 
\subsection{Storage}
We use this service just to store the profile pictures of each users that eventually uploaded it. 
\section{Google Cloud Platform}
\subsection{Google Maps}
It is probably the most important feature of this application, it allows to see and select the charging stations, visualised with a custom pin, check the own position and navigate on the map. Using Google Maps keeps the UI simple for the users because most of them already use it. 

The navigation point-to-point is kept outside the application because the free plan doesn't permit that feature. 
\section{Minor Packages}
\begin{itemize}
	\item \textbf{image\_picker}: it allows to upload images from the smartphone gallery, specifically for users that want to upload their profile pictures
	\item \textbf{email\_validator}: it is used to validate the email inserted by a user during registration process
	\item \textbf{url\_launcher}: it launches an external URL, we used it to launch the point-to-point navigation in Google Maps
	\item \textbf{sliding\_up\_panel}: we implemented a sliding up panel to visualise the charging stations by different order
	\item \textbf{flutter\_local\_notifications}: it is used to display push notification when a recharge is finished
	\item \textbf{background\_locator}: it gets location updates even when the application is killed, it's useful to check if the user has arrived at the selected charging station
\end{itemize}